### 2017-08-06 Tex_Dissertation/MSc_dissertation.tex
finishedbdt

\begin{figure}[ht!]
  \includegraphics[width=0.7\linewidth]{{images/postbdtcut}.pdf}
  \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application.}}
\end{figure}

@@

where $n_{data}$ are the number of events in the energy spectrum of the three jets after the TMVA (figure 4.12)
and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
of the histogram. The templates are summarised in the table below.

@@

@@

\begin{figure}[ht!]
\centering
  \includegraphics[width=0.7\linewidth]{{images/chisqvsmass_intlumi3000}.pdf}
  \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates.}}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
  \includegraphics[width=0.7\linewidth]{{images/postbdtcut}.pdf}
  \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application, again stacked.}}
\end{figure}

@@

where $n_{data}$ are the number of events in the energy spectrum of the three jets after the TMVA (figure 4.12)
and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
of the histogram. A $\chi^{2}$ was calculated for each different template, summarised in the table below.

@@

The mass was found  to be $m_{\tilde{t}}$ = 860 GeV.

@@

\begin{figure}[ht!]
\centering
  \includegraphics[width=0.7\linewidth]{{images/chisqvsmass_intlumi3000}.pdf}
  \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates. The minimum is at 
  860 GeV/c$^{2}$.}}
\end{figure}

@@

Using the Boosted Descision Trees and with the method of minimisation of the $\chi^{2}$ for different 
templates, I found the mass of the supersymmetric top quark to be

\begin{equation}
 m_{\tilde{t}}=860\pm 14 \textrm{GeV}/c^{2}
\end{equation}

Although the nominal mass is $M_{nom}$= 846 GeV/$c^{2}$, my calculation is one sigma  inside this range,
taking into account the aforementioned uncertainty at CLIC for integrated luminosity 
$\mathcal{L}_{int}$=3000 fb$^{-1}$.

\subsection{Classification Method: \textit{Gradient Boosted Descision Trees}}
